---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OPSR <img src="man/figures/logo.svg" align="right" height="139" alt="" />

<!-- badges: start -->
<!-- badges: end -->

Estimates ordered probit switching regression (OPSR) models - a Heckman type selection model with an ordinal selection and continuous outcomes. Different model specifications are allowed for each treatment/regime.

## Installation

Install from CRAN:

``` r
install.packages("OPSR")
```

You can install the development version of `OPSR` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dheimgartner/OPSR")
```

## Example

`OPSR` can be used whenever the ordinal treatment is not assigned exogenously but self-selected and one is interested in the treatment effect on a continuous outcome. The motivating example is telework frequency (conceptually, the treatment) and vehicle miles driven (the outcome of interest). We assume that two distinct processes lead people to choose a certain telework frequency and how mobile they are. Further and most importantly, the possibility of selection on unobservables exists. I.e., unobserved factors (as part of the errors of the two processes) might influence both the ordinal and continuous outcome. This leads to error correlation which needs to be accounted for in the modeling effort in spirit of Heckman.

```{r example}
library(OPSR)

f <-
  ## ordinal and continuous outcome
  twing_status | vmd_ln ~
  ## selection model
  edu_2 + edu_3 + hhincome_2 + hhincome_3 +
  flex_work + work_fulltime + twing_feasibility +
  att_proactivemode + att_procarowning +
  att_wif + att_proteamwork +
  att_tw_effective_teamwork + att_tw_enthusiasm + att_tw_location_flex |
  ## outcome model NTW
  female + age_mean + age_mean_sq +
  race_black + race_other +
  vehicle + suburban + smalltown + rural +
  work_fulltime +
  att_prolargehouse + att_procarowning +
  region_waa |
  ## outcome model NUTW
  edu_2 + edu_3 + suburban + smalltown + rural +
  work_fulltime +
  att_prolargehouse + att_proactivemode + att_procarowning |
  ## outcome model UTW
  female + hhincome_2 + hhincome_3 +
  child + suburban + smalltown + rural +
  att_procarowning +
  region_waa

fit <- opsr(f, telework_data, printLevel = 0)
texreg::screenreg(fit, beside = TRUE, include.pseudoR2 = TRUE, include.R2 = TRUE)
```
